Nirdizati: A Web-Based Tool for\\ Predictive Process Monitoring

### 2017-07-25 BPM17-demo-paper/paper.tex
dots, dots
first pass done

%\vspace{-\baselineskip}
\begin{figure}[t]%[H]
	\centering
	\includegraphics[width=0.7\textwidth]{img/nirdizati-overall}
	\caption{A high-level overview of Nirdizati.}
	\label{fig:nirdizati-overall}
\end{figure}
%\vspace{-\baselineskip}

@@

\begin{figure}[t!]%[H]
	\centering
	 \includegraphics[width=0.9\textwidth]{img/nirdizati-frontend}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{The front-end of Nirdizati Training.}
	\label{fig:nirdizati-frontend}
	\vspace{-0.5\baselineskip}
\end{figure}
\begin{figure}[b!]%[H]
	\centering
	 \includegraphics[width=0.8\textwidth]{img/nirdizati-training-architecture-rev}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{A high-level overview of Nirdizati Training.}
	\label{fig:nirdizati-training}
	\vspace{-0.5\baselineskip}
\end{figure}

Nirdizati Training is composed of a front-end application (\figurename~\ref{fig:nirdizati-frontend}), which allows users to configure the predictive models
and to assess the goodness-of-fit of the built models, and a back-end application responsible for the actual training and validation.
The back-end application is in turn composed of four submodules shown in \figurename~\ref{fig:nirdizati-training}.
A Log Manager is in charge of managing the logs. Uploading and retrieving the logs are the basic operations
of this module. The Encoder is responsible for parsing the logs, labeling them according to the desired type of prediction,
 and preparing the data for the training phase.
In the Training submodule, the encoded data are split into training and validation set used for evaluation purposes,
and the predictive models are built from the training data. Finally, the Evaluation submodule
tests the validation data against the model(s) created to get accuracy measures with respect to the ground truth,
available from the complete traces in the validation data.
The back-end application comes with a storage module for saving the uploaded logs and the built predictive models.

@@

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been trained, they are used by the Runtime component to make predictions for ongoing cases. As an input, Nirdizati Runtime takes a stream of events produced by information systems that register tasks performed in the organization (\figurename~\ref{fig:dfd_0}). Next, the produced stream is consumed by a web server which is responsible for storing data and further information processing.
The web server, in turn, communicates with a predictive engine which applies models obtained via Nirdizati Training for a business process and returns all the results of calculations.
After web server receives the outputs from each predictive model, it writes them to a database and updates corresponding clients.
From the user's side, the results are visualized via a dashboard-based interface which is capable of sending queries requesting various visualization options.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{img/dfd_0}
	\caption{High-level data flow diagram of Nirdizati Runtime}
	\label{fig:dfd_0}
\end{figure}
\vspace{-\baselineskip}

When a user logs into the system, she initially sees a table listing both currently ongoing cases (colored in gray) as well as completed cases (colored in green), as shown in \figurename~\ref{fig:nirdizati-runtime}. For each case, we provide a range of summary statistics including the number of completed events in a given case, case start time and the time of the latest event completion. For ongoing cases, we also estimated their completion time and a range of other process-specific indicators, such as the probability that a customer will not accept an offer from a salesperson. For completed cases, instead, we show the actual completion time and the actual indicators.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{img/nirdizati-runtime}
	\caption{Main view of Nirdizati Runtime}
	\label{fig:nirdizati-runtime}
	\vspace{-0.5\baselineskip}
\end{figure}
%\vspace{-\baselineskip}

Process workers and operational managers -- typical users of such system -- can set the process performance targets and subscribe to a stream of warnings and alerts generated whenever these targets are predicted to be violated. Thus, process workers will be capable of making more informed, data-driven decisions to get a better control of the process execution. This is especially beneficial for processes where process workers have more leeway to make corrective actions, for example, in a lead management process.

\section{Conclusion} \label{sec:conclusion}
The developed solution, named \emph{Nirdizati}, is a configurable full-stack web application that supports users in selecting the preferred prediction method from the list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process execution, are presented in a dashboard that offers multiple visualization options.

A video demo of Nirdizati can be found at \url{http://youtu.be/0nr14lX04-I}. A public release of Nirdizati Training and Nirdizati Runtime are available at \url{http://training.nirdizati.com} and \url{http://dashboard.nirdizati.com} respectively. The source code is available under the Lesser GNU Public License (LGPL) at \url{http://github.com/nirdizati}.
\bibliographystyle{splncs03}
\bibliography{paper}

>>>>

%\vspace{-\baselineskip}
\begin{figure}[t]%[H]
	\centering
	\includegraphics[width=0.7\textwidth]{img/nirdizati-overall}
	\caption{High-level overview of Nirdizati.}
	\label{fig:nirdizati-overall}
\end{figure}
%\vspace{-\baselineskip}

@@

\begin{figure}[t!]%[H]
	\centering
	 \includegraphics[width=0.9\textwidth]{img/nirdizati-frontend}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{Front-end of Nirdizati Training.}
	\label{fig:nirdizati-frontend}
	\vspace{-0.5\baselineskip}
\end{figure}
\begin{figure}[b!]%[H]
	\centering
	 \includegraphics[width=0.9\textwidth]{img/nirdizati-training-architecture-rev}
	%\includegraphics[width=0.7\textwidth]{img/nirdizati-training}
	\caption{High-level overview of Nirdizati Training.}
	\label{fig:nirdizati-training}
	\vspace{-0.5\baselineskip}
\end{figure}

Nirdizati Training is composed of a front-end application (\figurename~\ref{fig:nirdizati-frontend}), which allows users to configure the predictive models
and to assess the goodness-of-fit of the built models, and a back-end application responsible for the actual training and validation.
The back-end application is in turn composed of four submodules shown in \figurename~\ref{fig:nirdizati-training}.
A Log Manager is in charge of managing the logs. Uploading and retrieving the logs are the basic operations
of this module. The Encoder is responsible for parsing the logs, labeling them according to the desired type of prediction,
 and preparing the data for the training phase.
In the Training submodule, the encoded data is split into training and validation set used for evaluation purposes,
and the predictive models are built from the training data. Finally, the Evaluation submodule
tests the validation data against the model(s) created to get accuracy measures with respect to the ground truth,
available from the complete traces in the validation data.
The back-end application comes with a storage module for saving the uploaded logs and the built predictive models.

@@

\section{Nirdizati Runtime} \label{sec:runtime}
Once the predictive models have been trained, they are used by the Runtime component to make predictions on ongoing cases. As input, Nirdizati Runtime takes a stream of events produced by information systems that register the tasks performed in an organization (\figurename~\ref{fig:dfd_0}). The stream is processed by a web server.
In particular, the web server communicates with a predictive engine that queries the predictive models obtained by Nirdizati Training to get predictions about all the cases recorded in the event stream.
After the web server receives the predictions from each predictive model, it stores them into a database.
From the user's side, the results are visualized in a dashboard-based interface, which supports several visualization options.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.7\textwidth]{img/dfd_0}
	\caption{High-level data flow diagram of Nirdizati Runtime.}
	\label{fig:dfd_0}
\end{figure}
\vspace{-\baselineskip}

When a user logs into the system, she initially sees a table listing both currently ongoing cases (colored in gray) as well as completed cases (colored in green), as shown in \figurename~\ref{fig:nirdizati-runtime}. For each case, Nirdizati Runtime provides a range of summary statistics including the number of events in a given case, starting time of a case and the time when the latest event has occurred. For the ongoing cases, Nirdizati Runtime also estimates their completion time and a range of other process-specific indicators, such as the probability that a customer will not accept an offer from a salesperson. For completed cases, instead, it shows the actual completion time and the actual values of the indicators.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{img/nirdizati-runtime}
	\caption{Main view of Nirdizati Runtime.}
	\label{fig:nirdizati-runtime}
	\vspace{-0.5\baselineskip}
\end{figure}
%\vspace{-\baselineskip}

Process workers and operational managers -- typical users of Nirdizati -- can set the process performance targets and subscribe to a stream of warnings and alerts generated whenever these targets are predicted to be violated. Thus, they will be capable of making informed, data-driven decisions to get a better control of the process executions. This is especially beneficial for processes where process participants have more leeway to make corrective actions (for example, in a lead management process).

\section{Conclusion} \label{sec:conclusion}
Nirdizati is a configurable full-stack web application that supports users in selecting the preferred prediction method from a list of implemented methods and enables the continuous prediction of various performance indicators at runtime.
The results of the predictions, as well as the real-time summary statistics about the process executions, are presented in a dashboard that offers multiple visualization options.

A video demo of Nirdizati can be found at \url{http://youtu.be/0nr14lX04-I}. A public release of Nirdizati Training and Nirdizati Runtime are available at \url{http://training.nirdizati.com} and \url{http://dashboard.nirdizati.com}, respectively. The source code is available under the Lesser GNU Public License (LGPL) at \url{http://github.com/nirdizati}.
\bibliographystyle{splncs03}
\bibliography{paper}
